Descriptive adventures

### 2024-11-16 descriptivestry.Rmd
darkmodefixbug

<!DOCTYPE html>
<html lang="en">
<head>
    <meta charset="UTF-8">
    <meta name="viewport" content="width=device-width, initial-scale=1.0">
    <title>My Lab Journal</title>
    <link rel="stylesheet" href="styles.css">  <!-- Link to the CSS file I created for dark mode code chunks -->

</head>
<body>
    <header>
        <h1>Welcome to My Lab Journal</h1>
        <p>This is where I record my research and experiments.</p>
    </header>

    <main>
        <section>
            <h2>Experiment 1</h2>
            <p>Details of the first experiment go here.</p>
        </section>
        <section>
            <h2>Experiment 2</h2>
            <p>Details of the second experiment go here.</p>
        </section>
    </main>

    <footer>
        <p>Created by Me, 2024</p>
    </footer>
</body>
</html>

>>>>

<html lang="en">
<head>
    <meta charset="UTF-8">
    <meta name="viewport" content="width=device-width, initial-scale=1.0">
    <title>My Lab Journal</title>
    <link rel="stylesheet" href="styles.css">  <!-- Link to the CSS file I created for dark mode code chunks -->

</head>
</html>
